---
title: "InformeEventosYani"
output: html_document
date: "2025-10-04"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(patchwork)

donut_plot <- function(value, max_value, highlight_color, text_color) {
  # Wrangle data to get a data frame in the format we need it in to make our donut chart
  df <- tibble(x = 1, y = value) |>
    mutate(y_negative = max_value - y) |>
    pivot_longer(cols = -x)
  
  # Create a nicely formatted big number to go in the donut hole
  big_number_text_label <- value
  
  # Create our plot
  ggplot(
    df,
    aes(
      x = x,
      y = value,
      fill = name
    )
  ) +
    geom_col(show.legend = FALSE) +
    coord_polar(
      theta = "y",
      direction = -1
    ) +
    xlim(c(-2, 2)) +
    scale_fill_manual(values = c(highlight_color, "grey66")) +
    theme_void() +
    annotate("text",
             label = big_number_text_label,
             fontface = "bold",
             color = text_color,
             size = 12,
             x = -2,
             y = 0
    ) +
    theme(plot.title = element_text(color = text_color))
}

eventos <- read_csv("datos/EventosPorAnio2025.csv")

```

# Calculo totales

```{r}

total_events <- nrow(eventos)

events_by_format <- eventos |>
  group_by(Formato) |>
  summarise(numero = n()) |>
  arrange(desc(numero))

events_by_role <- eventos |>
  group_by(Rol) |>
  summarise(numero = n()) |>
  arrange(desc(numero))

events_by_type <- eventos |>
  group_by(Tipo) |>
  summarise(numero = n()) |>
  arrange(desc(numero))

totales_year <- eventos |>
  group_by(anio) |>
  summarise(numero = n()) |>
  arrange(anio)


totales_rol <- eventos |>
  group_by(Rol) |>
  summarise(numero = n()) |>
  arrange(desc(numero))

totales_tipo <- eventos |>
  group_by(Tipo) |>
  summarise(numero = n()) |>
  arrange(desc(numero))

```



```{r}


p2 <- donut_plot(496, 496, "orange", "black") + labs(title = "Total Events")

p4 <- donut_plot(267, 496, "lightblue2", "black") + labs(title = "Online Events")

p5 <- donut_plot(32, 47, "#216E39", "black") + labs(title = "Active Years")


```


# Graficos las otras variables

```{r}
p1 <- totales_year |>
  ggplot(aes(x=anio, y=numero)) +
  geom_line(color = "blue", size=2) +
  labs(title = "Total Events by Year",
       y = "",
       x = "") +
  scale_x_continuous(breaks = c(1993, 1997, 2001, 2005, 2009, 2013, 2017, 2021, 2025)) +
  theme_minimal() 


p0 <- totales_rol |>
  ggplot(aes(x=fct_reorder(Rol, numero), y= numero)) +
  geom_col(fill = "#0072B2") +
  coord_flip() +
  labs(title = "Total Events by Role",
       y = "",
       x = "") +
  theme_minimal()

p6 <- totales_tipo |>
  ggplot(aes(x=fct_reorder(Tipo, numero), y= numero)) +
  geom_col(fill = "#56B4E9") +
  coord_flip() +
  labs(title = "Total Events by Type",
       y = "",
       x = "") +
  theme_minimal()


```
## Panel final

```{r}
(p2 | p4 | p5) / (p1 / (p0 | p6))
```



Here's a logical grouping of these event types with totals and explanations:

## **Teaching & Training Events (Total: 192)**
- **Course (192)** - Structured educational programs with multiple sessions focused on teaching specific skills or knowledge

## **Presentations & Talks (Total: 186)**
- **Invited Talk (73)** - Presentations by guests specifically requested to share their expertise
- **Regular Talk (63)** - Standard presentations or lectures, typically part of a regular program
- **Keynote (19)** - High-profile opening or closing speeches at major events, usually by distinguished speakers
- **Lightning Talk (10)** - Brief, time-limited presentations (typically 5-10 minutes)
- **Panel (25)** - Group discussions with multiple experts addressing a topic together
- **Sponsor Talk (1)** - Presentations by event sponsors

## **Large-Scale Events (Total: 58)**
- **Conference (35)** - Multi-day gatherings with multiple sessions, speakers, and networking opportunities
- **Hackathon (3)** - Intensive collaborative coding events, typically 24-48 hours
- **Exhibition (19)** - Showcases or demonstrations of work, projects, or products
- **Contest (1)** - Competitive events with winners

## **Community & Collaborative Events (Total: 55)**
- **Podcast (22)** - Audio recordings of discussions, interviews, or presentations
- **Community Call (12)** - Regular virtual or in-person gatherings for community members to connect
- **Coworking (13)** - Shared working sessions where participants work alongside each other
- **Book Club (8)** - Group discussions centered around reading and analyzing books

**Grand Total: 491 events**



## Reporte de publicaciones


```{r}
library(tidyverse)

PublicacionesPorAnioYanina <- read_csv("datos/PublicacionesPorAnioYanina2025.csv")

pub_xtipoxanio <- PublicacionesPorAnioYanina %>% 
  mutate(Type = case_when(
    Type == "National Conferences" ~ "Conferences",
    Type == "International Conferences" ~ "Conferences",
    Type == "Book Chapters" ~ "Book",
    TRUE ~ Type
  )) %>% 
  count(Year, Type)

pub_x_tipo <- PublicacionesPorAnioYanina |> 
  count(Type)
```

# Graficos

```{r}
p <- ggplot(pub_xtipoxanio, aes(x = Year, y = Type, fill = n ))

pub <- p + geom_tile() +
  theme_minimal() +
  scale_x_continuous(breaks = seq(1998, 2025, by = 2), expand = c(0, 0)) +
  scale_y_discrete(expand = c(0, 0)) +
  scale_fill_gradientn(colours = c("yellow", "green", "darkgreen")) +
  coord_equal() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        legend.position = 'bottom')
```




